Data_Analysis_MS_ddm_exp1

### 2018-07-05 Results/preproc/MS_ddm_preproc.rmd
finished exp1 preproc

---
title: "Data_Analysis_exp7"
author: "hcp"
date: "2017-12"
output: word_document
---
<style type="text/css">

@@

```{r Initializing, include=FALSE}
source('Initial.r')
curDir  <- dirname(rstudioapi::getSourceEditorContext()$path)   # directory for preprocessing
rootDir <- gsub('.{7}$', '', curDir)
#rawDir <- paste(curDir,'/data/',sep = '')
traDir <- paste(rootDir,'Traditional_Analysis',sep = '')
ddmDir <- paste(rootDir,'HDDM',sep = '')
```

```{r loadingData_e7,echo=FALSE,results='hide'}
df.M <- read.csv("MS_matchTask_raw.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) # data for matching task
df.C <- read.csv("MS_categTask_raw.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)  # data for categorization task

@@

# exlude subject criterion 2: less than 50% overall accuracy
# change no response to error
df.M.tmp <- df.M
df.M.tmp$ACC[df.M.tmp$ACC == -1] <- 0
df.C.tmp <- df.C
df.C.tmp$ACC[df.C.tmp$ACC == -1] <- 0

@@

excldSub2.M <- df.M.acc.g$Subject[df.M.acc.g$ACC < 0.5]      # less 50% accuracy in matching task
excldSub2.C <- df.C.acc.g$Subject[df.C.acc.g$ACC < 0.5]      # less than 50% accuracy in categorization task
df.M.valid <- df.M[!(df.M$Subject %in% excldSub2.M),]        # exclude the invalid subjects
df.C.valid <- df.C[!(df.C$Subject %in% excldSub2.C),]
df.C.valid <- df.C.valid[!(df.C.valid$Subject %in% excldSub2.C),]
rm(df.M,df.C,df.M.tmp,df.C.tmp)
```

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# clean data for traditional analysis
df.M1 <- df.M.valid
df.C1 <- df.C.valid
df.M1$RT <- df.M1$RT * 1000 # transfer from seconds to min seconds
df.C1$RT <- df.C1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian

@@

# get the data file for hddm analysis
df.M.ddm.v <- df.M.valid   # exclude the invalid subjects
df.C.ddm.v <- df.C.valid

@@

setwd(ddmDir)
write.csv(df.M.hddm_m,'MS_match_hddm.csv',row.names = F)
write.csv(df.M.hddm_nm,'MS_mismatch_hddm.csv',row.names = F)
write.csv(df.C.hddm_val,'MS_categ_val_hddm.csv',row.names = F)
write.csv(df.C.hddm_id,'MS_categ_id_hddm.csv',row.names = F)
setwd(curDir)
rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
```
## Participants
`r numT.subj+length(excldSub1)` college students (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`) participated in experiment 7. All partcipants were right handed, and all had normal or corrected-to-normal vision. Informed consent was obtained from all partcipants prior to the experiment according to procedure approved by a local ethics committee. Data of `r length(excldSub1)` participants were excluded from matching task because of the procedura failure, and `r num.excld.sub` of the participants data were excluded from the analysis for matching task and categorization task because of less than 50% overall accuracy for the matching task, leaving `r numT.subj - num.excld.sub` participants (`r numV.female` female, age: `r ageV.mean` $\pm$ `r ageV.std` years) for matching task. `r num.excld.sub.T` addtional participants's data in categorization task were excluded becasue of less than 50% accuracy for the categorization task,leaving `r numT.subj - num.excld.sub - num.excld.sub.T` participants (`r numV.female.T` female, age: `r ageV.mean.T` $\pm$ `r ageV.std.T` years) for categorization task.

##Results 
For the learning phase, we excluded the first 24 trials, which is suppose to be the duration participants were practicing. Also, trials that responsed less than 200 ms or no-response was excluded.For the learning phase, `r round(ratio.excld.trials.L,4)` of the total trials was excluded, for the testing phase, `r round(ratio.excld.trials.T,4)` of the total trials was excluded.

### Results of Learning phase
#### Analaysis of d prime
```{r analyzing for d prime_e7_match, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
## calculate the d prime for each condition
# calculate the number of hit,CR,miss or FA 
df.M1.V$sdt <- NA
for (i in 1:nrow(df.M1.V)){
        if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "match" & !is.na(df.M1.V$ResponseKey[i])){
                df.M1.V$sdt[i] <- "hit"
        } else if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "nonmatch" & !is.na(df.M1.V$ResponseKey[i])){
                df.M1.V$sdt[i] <- "CR"
        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "match" & !is.na(df.M1.V$ResponseKey[i])){
                df.M1.V$sdt[i] <- "miss"
        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "nonmatch" & !is.na(df.M1.V$ResponseKey[i])){
                df.M1.V$sdt[i] <- "FA"
        }
}

# calculate the number of each for each condition
df.M1.V.SDT <-  ddply(df.M1.V,.(Subject,Morality, Identity,sdt), summarise, N = length(sdt))
df.M1.V.SDT <- df.M1.V.SDT[complete.cases(df.M1.V.SDT$sdt),] # exclude NA, which represents no-response trials

# long format to wide
df.M1.V.SDT_w <- dcast(df.M1.V.SDT, Subject + Morality + Identity ~ sdt,value.var = "N")
df.M1.V.SDT_w$miss[is.na(df.M1.V.SDT_w$miss)] <- 0 # transfer NA to 0
df.M1.V.SDT_w$FA[is.na(df.M1.V.SDT_w$FA)]     <- 0
df.M1.V.SDT_w$hitR <- df.M1.V.SDT_w$hit/(df.M1.V.SDT_w$hit + df.M1.V.SDT_w$miss)
df.M1.V.SDT_w$faR <- df.M1.V.SDT_w$FA/(df.M1.V.SDT_w$FA + df.M1.V.SDT_w$CR)

@@

# transfor from long format to wide format
df.M1.V.SDT_ww <- dcast(df.M1.V.SDT_w, Subject ~ Identity + Morality ,value.var = "dprime")

# anova for d prime with 2*2 design
e7_L.d_anova <- ezANOVA(df.M1.V.SDT_w,dv = dprime, wid = Subject, within=.(Morality,Identity), type=3)

df.M1.V.SDT_w$Subject <- factor(df.M1.V.SDT_w$Subject)  # make the subject "factor"

# using Bayesfactor analysis (which is not reported in the document)
e7_L.dprime_anova_bf  <- anovaBF(dprime ~ Morality*Identity + Subject, data = df.M1.V.SDT_w, whichRandom = "Subject")

# Good self vs Bad self
e7_L.d.t.good_bad_slf <- t.test(df.M1.V.SDT_ww$Self_Good,df.M1.V.SDT_ww$Self_Bad,paired = TRUE)     # t-test
df.M1.V.SDT_ww$good_bad_slf <- df.M1.V.SDT_ww$Self_Good - df.M1.V.SDT_ww$Self_Bad                   # calculate the differences
e7_L.d.t.good_bad_slf.CI <- bootES(df.M1.V.SDT_ww$good_bad_slf,R = 20000, effect.type = "cohens.d") # calculate the cI using BootES

# give new names for each key information, for later use in the markdown
e7_L.d.tvalue.good_bad_slf <- round(as.numeric(e7_L.d.t.good_bad_slf[[1]]),3)
e7_L.d.df.M1.good_bad_slf <- as.numeric(e7_L.d.t.good_bad_slf[[2]])
e7_L.d.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_slf[[3]]),"bonferroni",4)
e7_L.d.cohens.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[1]],4) 
e7_L.d.CI.L.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][1],4)
e7_L.d.CI.H.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][2],4)

# Good other vs. Bad other
e7_L.d.t.good_bad_oth <- t.test(df.M1.V.SDT_ww$Other_Good,df.M1.V.SDT_ww$Other_Bad,paired = TRUE)
df.M1.V.SDT_ww$good_bad_oth <- df.M1.V.SDT_ww$Other_Good - df.M1.V.SDT_ww$Other_Bad
e7_L.d.t.good_bad_oth.CI <- bootES(df.M1.V.SDT_ww$good_bad_oth,R = 20000, effect.type = "cohens.d")

e7_L.d.tvalue.good_bad_oth  <- round(as.numeric(e7_L.d.t.good_bad_oth[[1]]),3)
e7_L.d.df.M1.good_bad_oth  <- as.numeric(e7_L.d.t.good_bad_oth[[2]])
e7_L.d.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_oth[[3]]),"bonferroni",4)
e7_L.d.cohens.good_bad_oth <- round(e7_L.d.t.good_bad_oth.CI[[1]],4) 
e7_L.d.CI.L.good_bad_oth <- round(e7_L.d.t.good_bad_oth.CI[[12]][1],4)
e7_L.d.CI.H.good_bad_oth <- round(e7_L.d.t.good_bad_oth.CI[[12]][2],4)

# Good self vs Good other
e7_L.d.t.slf_oth_good <- t.test(df.M1.V.SDT_ww$Self_Good,df.M1.V.SDT_ww$Other_Good,paired = TRUE)
df.M1.V.SDT_ww$slf_oth_good <- df.M1.V.SDT_ww$Self_Good - df.M1.V.SDT_ww$Other_Good
e7_L.d.t.slf_oth_good.CI <- bootES(df.M1.V.SDT_ww$slf_oth_good,R = 20000, effect.type = "cohens.d")

e7_L.d.tvalue.slf_oth_good  <- round(as.numeric(e7_L.d.t.slf_oth_good[[1]]),3)
e7_L.d.df.M1.slf_oth_good  <- as.numeric(e7_L.d.t.slf_oth_good[[2]])
e7_L.d.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_L.d.t.slf_oth_good[[3]]),"bonferroni",4)
e7_L.d.cohens.slf_oth_good <- round(e7_L.d.t.slf_oth_good.CI[[1]],4) 
e7_L.d.CI.L.slf_oth_good <- round(e7_L.d.t.slf_oth_good.CI[[12]][1],4)
e7_L.d.CI.H.slf_oth_good <- round(e7_L.d.t.slf_oth_good.CI[[12]][2],4)

# Bad self vs. Bad other
e7_L.d.t.slf_oth_bad <- t.test(df.M1.V.SDT_ww$Self_Bad,df.M1.V.SDT_ww$Other_Bad,paired = TRUE)
df.M1.V.SDT_ww$slf_oth_bad <- df.M1.V.SDT_ww$Self_Bad - df.M1.V.SDT_ww$Other_Bad
e7_L.d.t.slf_oth_bad.CI <- bootES(df.M1.V.SDT_ww$slf_oth_bad,R = 20000, effect.type = "cohens.d")

e7_L.d.tvalue.slf_oth_bad  <- round(as.numeric(e7_L.d.t.slf_oth_bad[[1]]),3)
e7_L.d.df.M1.slf_oth_bad <- as.numeric(e7_L.d.t.slf_oth_bad[[2]])
e7_L.d.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_L.d.t.slf_oth_bad[[3]]),"bonferroni",4)
e7_L.d.cohens.slf_oth_bad <- round(e7_L.d.t.slf_oth_bad.CI[[1]],4) 
e7_L.d.CI.L.slf_oth_bad <- round(e7_L.d.t.slf_oth_bad.CI[[12]][1],4)
e7_L.d.CI.H.slf_oth_bad <- round(e7_L.d.t.slf_oth_bad.CI[[12]][2],4)

#####save the dprime and ACC data for late used ####
colnames(df.M1.V.SDT_ww) <- paste("L_d", colnames(df.M1.V.SDT_ww), sep = "_")
write.csv(df.M1.V.SDT_ww,"data_matching_v_dprime.csv",row.names=FALSE)
df.M1.V.acc <-  ddply(df.M1.V,.(Subject,Match,Identity,Morality), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))
df.M1.V.acc_w <- dcast(df.M1.V.acc, Subject ~ Match + Identity + Morality ,value.var = "ACC")
df.M1.V.acc_w$good_bad_slf <- df.M1.V.acc_w$match_Self_Good - df.M1.V.acc_w$match_Self_Bad
df.M1.V.acc_w$good_oth <- df.M1.V.acc_w$match_Other_Good - df.M1.V.acc_w$match_Other_Bad
df.M1.V.acc_w$slf_oth_good <- df.M1.V.acc_w$match_Self_Good - df.M1.V.acc_w$match_Other_Good
df.M1.V.acc_w$slf_oth_bad <- df.M1.V.acc_w$match_Self_Bad - df.M1.V.acc_w$match_Other_Bad

colnames(df.M1.V.acc_w) <- paste("L_acc", colnames(df.M1.V.acc_w), sep = "_")
colnames(df.M1.V.acc_w)[colnames(df.M1.V.acc_w) == 'L_acc_Subject'] <- 'Subject'
write.csv(df.M1.V.acc_w,"data_matching_v_acc.csv",row.names=FALSE)
##### save data for later analysis ####

df.M1.V.SDT.sum      <- summarySE(df.M1.V.SDT_w,measurevar = 'dprime',groupvars = c('Morality','Identity'))
e7_L.d.mean.GoodSelf <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Self'],3)
e7_L.d.sd.GoodSelf   <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Self'],3)
e7_L.d.mean.BadSelf  <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Self'],3)
e7_L.d.sd.BadSelf    <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Self'],3)

e7_L.d.mean.GoodOther <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Other'],3)
e7_L.d.sd.GoodOther   <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Other'],3)
e7_L.d.mean.BadOther  <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Other'],3)
e7_L.d.sd.BadOther    <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Other'],3)

e7_L.p_dprime1 <- ggplot(data = df.M1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3,width = .6) +    # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
                      #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = 1,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'self-referential',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme  + 
        theme(axis.text = element_text (size = 24,color = 'black')) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good   ","Bad"))+
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

>>>>

---
title: "Data_Analysis_MS_ddm_exp1"
author: "hcp"
date: "2017-12"
output: word_document
---
<style type="text/css">

@@

```{r Initializing, include=FALSE}
source('Initial.r')
curDir  <- getwd()
#curDir  <- dirname(rstudioapi::getSourceEditorContext()$path)   # directory for preprocessing
rootDir <- gsub('.{7}$', '', curDir)
#rawDir <- paste(curDir,'/data/',sep = '')
traDir <- paste(rootDir,'Traditional_Analysis',sep = '')
ddmDir <- paste(rootDir,'HDDM',sep = '')
```

```{r loadingData_MS_ddm_exp1,echo=FALSE,results='hide'}
df.M <- read.csv("MS_matchTask_raw.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) # data for matching task
df.C <- read.csv("MS_categTask_raw.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)  # data for categorization task

subTotl <- unique(df.M$Subject)

@@

# exlude subject criterion 2: less than 50% overall accuracy
# change no response to error
df.M.tmp <- df.M
df.M.tmp$ACC[df.M.tmp$ACC == -1] <- 0
df.C.tmp <- df.C
df.C.tmp$ACC[df.C.tmp$ACC == -1] <- 0 # this was not done in previous analysis, resulting the wronly excluded participants in registration

@@

excldSub2.M <- df.M.acc.g$Subject[df.M.acc.g$ACC < 0.5]      # < 50% accuracy in matching task
excldSub2.C <- df.C.acc.g$Subject[df.C.acc.g$ACC < 0.5]      # < 50% accuracy in categorization task
df.M.valid <- df.M[!(df.M$Subject %in% excldSub2.M),]        # exclude the invalid subjects
df.C.valid <- df.C[!(df.C$Subject %in% excldSub2.M),]
df.C.valid <- df.C.valid[!(df.C.valid$Subject %in% excldSub2.C),]
rm(df.M,df.C,df.M.tmp,df.C.tmp)
```

```{r clean the data,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# clean data for traditional analysis
df.M1 <- df.M.valid
df.C1 <- df.C.valid
df.M1$RT <- df.M1$RT * 1000 # transfer from seconds to min seconds
df.C1$RT <- df.C1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian

@@

# get the data file for hddm analysis ####
df.M.ddm.v <- df.M.valid   # exclude the invalid subjects
df.C.ddm.v <- df.C.valid

@@

setwd(ddmDir)
write.csv(df.M.hddm_m,'MS_match_hddm.csv',row.names = F)
write.csv(df.M.hddm_nm,'MS_mismatch_hddm.csv',row.names = F)
write.csv(df.C.hddm_val,'MS_categ_val_hddm.csv',row.names = F)
write.csv(df.C.hddm_id,'MS_categ_id_hddm.csv',row.names = F)
setwd(curDir)
rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
```
## Participants
`r length(subTotl)` college students (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`) participated in this experiment. All partcipants were right handed, and all had normal or corrected-to-normal vision. Informed consent was obtained from all partcipants prior to the experiment according to procedure approved by a local ethics committee. Data of `r length(excldSub1)` participants were excluded from matching task because of the procedura failure, and `r length(excldSub2.M)` of the participants data were excluded from the analysis for matching task and categorization task because of less than 50% overall accuracy for the matching task, leaving `r nrow(df.M1.V.basic)` participants (`r numV.female` female, age: `r ageV.mean` $\pm$ `r ageV.std` years) for matching task. `r length(excldSub2.C)` addtional participants's data in categorization task were excluded becasue of less than 50% accuracy for the categorization task,leaving `r nrow(df.C1.V.basic)` participants (`r numV.female.C` female, age: `r ageV.mean.C` $\pm$ `r ageV.std.C` years) for categorization task.

##Results 
For the learning phase, we excluded the first 24 trials, which is suppose to be the duration participants were practicing. Also, trials that responsed less than 200 ms or no-response was excluded.For the learning phase, `r round(ratio.excld.trials.M,4)` of the total trials was excluded, for the testing phase, `r round(ratio.excld.trials.C,4)` of the total trials was excluded.

#### Analaysis of d prime
```{r analyzing for match task, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
### ACC ####
df.M1.V.acc  <-  plyr::ddply(df.M1.V,.(Subject, Match, Morality, Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

df.M1.V.acc_w <- dcast(df.M1.V.acc, Subject ~ Match + Morality + Identity,value.var = "ACC")

# rename the column number
colnames(df.M1.V.acc_w)[2:9] <- paste("ACC", colnames(df.M1.V.acc_w[,2:9]), sep = "_")

## calculate the d prime for each condition
# calculate the number of hit,CR,miss or FA 
df.M1.V$sdt <- NA
for (i in 1:nrow(df.M1.V)){
        if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "match"){
                df.M1.V$sdt[i] <- "hit"
        } else if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "nonmatch" ){
                df.M1.V$sdt[i] <- "CR"
        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "match"){
                df.M1.V$sdt[i] <- "miss"
        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "nonmatch" ){
                df.M1.V$sdt[i] <- "FA"
        }
}

# calculate the number of each for each condition
df.M1.V.SDT <- plyr::ddply(df.M1.V,.(Subject,Age, Gender, Morality, Identity,sdt), summarise, N = length(sdt))
df.M1.V.SDT <- df.M1.V.SDT[complete.cases(df.M1.V.SDT$sdt),] # exclude NA, which represents no-response trials

# long format to wide
df.M1.V.SDT_w <- reshape2::dcast(df.M1.V.SDT, Subject + Age + Gender + Morality + Identity ~ sdt,value.var = "N")
df.M1.V.SDT_w$miss[is.na(df.M1.V.SDT_w$miss)] <- 0 # transfer NA to 0
df.M1.V.SDT_w$FA[is.na(df.M1.V.SDT_w$FA)]     <- 0
df.M1.V.SDT_w$hitR <- df.M1.V.SDT_w$hit/(df.M1.V.SDT_w$hit + df.M1.V.SDT_w$miss)
df.M1.V.SDT_w$faR <- df.M1.V.SDT_w$FA/(df.M1.V.SDT_w$FA + df.M1.V.SDT_w$CR)

@@

# transfor from long format to wide format
df.M1.V.SDT_ww <- dcast(df.M1.V.SDT_w, Subject + Age + Gender ~ Morality + Identity ,value.var = "dprime")
# rename the column number
colnames(df.M1.V.SDT_ww)[4:7] <- paste("d", colnames(df.M1.V.SDT_ww[,4:7]), sep = "_")

df.M1.V.SDT_l <- df.M1.V.SDT_w[,c(1:5,12)]

# preproc RT data ####
df.M1.V.RT <- df.M1.V[df.M1.V$ACC == 1,]

# get the summary results
df.M1.V.RT.subj <- summarySEwithin(df.M1.V.RT,measurevar = 'RT', withinvar = c('Subject','Match','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)
df.M1.V.RT.subj_w <- dcast(df.M1.V.RT.subj, Subject ~ Match + Morality + Identity ,value.var = "RT")

# rename the columns of RT data
colnames(df.M1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.M1.V.RT.subj_w[,2:9]), sep = "_")

## saving data ####
# merge the dprime and RT data and save
df.M1.V.sum_w <- merge(df.M1.V.acc_w,  df.M1.V.SDT_ww,by = "Subject")
df.M1.V.sum_w <- merge(df.M1.V.sum_w,df.M1.V.RT.subj_w,by = 'Subject')

# merge the RT and ACC data (long-format)
df.M1.V.sum_rt_acc_l <- merge(df.M1.V.acc,df.M1.V.RT.subj,by = c("Subject","Match","Morality",'Identity'))
df.M1.V.sum_rt_acc_l <- df.M1.V.sum_rt_acc_l[order(df.M1.V.sum_rt_acc_l$Subject),]

df.M1.V.sum_rt_acc_l <- df.M1.V.sum_rt_acc_l[,c("Subject","Match","Morality",'Identity',"N.x","countN","ACC","RT")]
colnames(df.M1.V.sum_rt_acc_l) <- c("Subject","Match","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")

# order the columns
df.M1.V.sum_w <- df.M1.V.sum_w[,c(colnames(df.M1.V.sum_w)[c(1,10:11,2:9,12:23)])]

# calculate the effect of self-ref and valence
df.M1.v.sum_eff_w <- df.M1.V.sum_w[,1:3]
df.M1.v.sum_eff_w$d_Good_Self_Other <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
df.M1.v.sum_eff_w$d_Self_Good_Bad   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self

df.M1.v.sum_eff_w$RT_Good_Self_Other <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
df.M1.v.sum_eff_w$RT_Self_Good_Bad   <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self

# write files
setwd(traDir)
write.csv(df.M1.V.sum_w,'MS_match_behav_wide.csv',row.names = F)
write.csv(df.M1.V.SDT_l,'MS_match__dprime_long.csv',row.names = F)
write.csv(df.M1.V.sum_rt_acc_l,'MS_match__rt_acc_long.csv',row.names = F)
setwd(curDir)
#ggsave("e7_L.p_rt2.pdf", e7_L.p_rt2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
```

```{r preproc MS_categ_task,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.C1.V.acc <- plyr::ddply(df.C1.V,.(Subject,Age, Gender, Task,Morality,Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

# wide-format
df.C1.V.acc_w  <- dcast(df.C1.V.acc, Subject ~ Task + Morality + Identity ,value.var = "ACC")

# rename the column number
colnames(df.C1.V.acc_w)[2:9] <- paste("ACC", colnames(df.C1.V.acc_w[,2:9]), sep = "_")

# combing data from diff task for analyzing the interaction btw val and id
df.C1.V.acc_noTask  <-  plyr::ddply(df.C1.V,.(Subject, Morality, Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

df.C1.V.acc_noTask_w <- dcast(df.C1.V.acc_noTask, Subject ~ Morality + Identity,value.var = "ACC")
# rename the column number
colnames(df.C1.V.acc_noTask_w)[2:5] <- paste("ACC", colnames(df.C1.V.acc_noTask_w[,2:5]), sep = "_")

# combine data cross task
# tmp <- aggregate(df.C1.V.acc[,7],list(df.C1.V.acc$Subject,df.C1.V.acc$Morality,df.C1.V.acc$Identity),mean)
df.C1.V.acc.noTask <- summarySE(df.C1.V.acc,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
df.C1.V.acc.noTask_w <- dcast(df.C1.V.acc.noTask, Subject ~  Morality + Identity  ,value.var = "ACC")

df.C1.V.acc.noTask_w$good_bad_slf <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Bad_Self
df.C1.V.acc.noTask_w$good_bad_oth <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Bad_Other
df.C1.V.acc.noTask_w$slf_oth_good <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Good_Other
df.C1.V.acc.noTask_w$slf_oth_bad <- df.C1.V.acc.noTask_w$Bad_Self - df.C1.V.acc.noTask_w$Bad_Other

## preprocessing RT data
df.C1.V.RT <- df.C1.V[df.C1.V$ACC == 1,]  # exclued inaccurate data
df.C1.V.RT.subj <- summarySEwithin(df.C1.V.RT,measurevar = 'RT', withinvar = c('Subject','Task','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
df.C1.V.RT.subj_w <- dcast(df.C1.V.RT.subj, Subject ~ Task + Morality + Identity ,value.var = "RT")

# rename the columns of RT data
colnames(df.C1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.C1.V.RT.subj_w[,2:9]), sep = "_")

# combining data form different task for analyszing interaction of val and id
df.C1.V.RT.subj_noTask <- summarySEwithin(df.C1.V.RT,measurevar = 'RT', withinvar = c('Subject','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
df.C1.V.RT.subj_noTask_w <- dcast(df.C1.V.RT.subj_noTask, Subject ~ Morality + Identity ,value.var = "RT")

# rename the columns of RT data
colnames(df.C1.V.RT.subj_noTask_w)[2:5] <- paste("RT", colnames(df.C1.V.RT.subj_noTask_w[,2:5]), sep = "_")

## saving data ####
# merge the accuracy and RT data and save
df.C1.V.sum_w <- merge(df.C1.V.acc_w,  df.C1.V.RT.subj_w,by = "Subject")
df.C1.V.sum_noTask_w <- merge(df.C1.V.acc_noTask_w,  df.C1.V.RT.subj_noTask_w,by = "Subject")

# calculate the effect of self-ref and valence
df.C1.v.sum_eff_w <- data.frame(df.C1.V.sum_w[,c('Subject')])
colnames(df.C1.v.sum_eff_w) <- 'Subject'
df.C1.v.sum_eff_w$RT_Val_Good_selfEffect <- df.C1.V.sum_w$RT_Val_Good_Other - df.C1.V.sum_w$RT_Val_Good_Self
df.C1.v.sum_eff_w$RT_Val_Self_valEffect  <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Good_Self
df.C1.v.sum_eff_w$RT_Id_Good_selfEffect  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
df.C1.v.sum_eff_w$RT_Id_Self_valEffect   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self

df.C1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.C1.V.sum_w$ACC_Val_Good_Other - df.C1.V.sum_w$ACC_Val_Good_Self
df.C1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.C1.V.sum_w$ACC_Val_Bad_Self - df.C1.V.sum_w$ACC_Val_Good_Self
df.C1.v.sum_eff_w$ACC_Id_Good_selfEffect  <- df.C1.V.sum_w$ACC_Id_Good_Other - df.C1.V.sum_w$ACC_Id_Good_Self
df.C1.v.sum_eff_w$ACC_Id_Self_valEffect   <- df.C1.V.sum_w$ACC_Id_Bad_Self - df.C1.V.sum_w$ACC_Id_Good_Self

# merge the effect file
df.v.sum_eff_all_w <- merge(df.M1.v.sum_eff_w,df.C1.v.sum_eff_w,by="Subject")

# merge the RT and ACC data (long-format) ####
df.C1.V.sum_rt_acc_l <- merge(df.C1.V.acc,df.C1.V.RT.subj,by = c("Subject","Task","Morality",'Identity'))
df.C1.V.sum_rt_acc_l <- df.C1.V.sum_rt_acc_l[order(df.C1.V.sum_rt_acc_l$Subject),]

df.C1.V.sum_rt_acc_l <- df.C1.V.sum_rt_acc_l[,c("Subject","Task","Morality",'Identity',"N.x","countN","ACC","RT")]
colnames(df.C1.V.sum_rt_acc_l) <- c("Subject","Task","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_categ__rt_acc_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

```{r plot_match_data,echo=FALSE,warning=FALSE, message=FALSE}
#plot the rT data from matching task
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)

# plot the dprime data from matching task
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
